---
title: "P8130_hw2"
author: "Zhiqian Fang zf2212"
date: "9/25/2018"
output: html_document
---

_Load library and clean up workspace_
```{r}
library(tidyverse)

rm(list=ls())
```

_Import data_
```{r}
migraine_data = readxl::read_xlsx("./Migraine.xlsx") %>% 
  janitor::clean_names()
```

_Creat subsets of NDDIE and CSED_
```{r}
nddie_16up = filter(migraine_data, nddie >= 16)
nddie_16low = filter(migraine_data, nddie < 16)
cesd_16up = filter(migraine_data, cesd >= 16)
cesd_16low = filter(migraine_data, cesd < 16)
```

### Summarize the three variables for epilepsy patients with and without migraine


_Summary of CESD_
```{r}
sum_cesd = migraine_data %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(cesd, na.rm = TRUE),
    sd = sd(cesd, na.rm = TRUE),
    med = median(cesd, na.rm = TRUE),
    max = max(cesd, na.rm = TRUE),
    min = min(cesd, na.rm = TRUE),
    missval = sum(is.na.data.frame(cesd)),
    samp_size = length((cesd)[!is.na(cesd)])
  )
sum_cesd
```


_Summary of CESD lower than 16_
```{r}
sum_cesd_16low = cesd_16low %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(cesd, na.rm = TRUE),
    sd = sd(cesd, na.rm = TRUE),
    med = median(cesd, na.rm = TRUE),
    max = max(cesd, na.rm = TRUE),
    min = min(cesd, na.rm = TRUE),
    missval = sum(is.na.data.frame(cesd)),
    samp_size = length((cesd)[!is.na(cesd)])
    )
sum_cesd_16low
```


_Summary of CESD higher than 16_


```{r}
sum_cesd_16up = cesd_16up %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(cesd, na.rm = TRUE),
    sd = sd(cesd, na.rm = TRUE),
    med = median(cesd, na.rm = TRUE),
    max = max(cesd, na.rm = TRUE),
    min = min(cesd, na.rm = TRUE),
    missval = sum(is.na.data.frame(cesd)),
    samp_size = length((cesd)[!is.na(cesd)])
    ) 
sum_cesd_16up
```


_Summary of NDDIE_
```{r}
sum_nddie = migraine_data %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(nddie, na.rm = TRUE),
    sd = sd(nddie, na.rm = TRUE),
    med = median(nddie, na.rm = TRUE),
    max = max(nddie, na.rm = TRUE),
    min = min(nddie, na.rm = TRUE),
    missval = sum(is.na.data.frame(nddie)),
    samp_size = length((nddie)[!is.na(nddie)])
  ) 
sum_nddie
```


_Summary of NDDIE lower than 16_
```{r}
sum_nddie_16low = nddie_16low %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(nddie, na.rm = TRUE),
    sd = sd(nddie, na.rm = TRUE),
    med = median(nddie, na.rm = TRUE),
    max = max(nddie, na.rm = TRUE),
    min = min(nddie, na.rm = TRUE),
    missval = sum(is.na.data.frame(nddie)),
    samp_size = length((nddie)[!is.na(nddie)])
  )
sum_nddie_16low
```


_Summary of NDDIE higher than 16_
```{r}
sum_nddie_16up = nddie_16up %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(nddie, na.rm = TRUE),
    sd = sd(nddie, na.rm = TRUE),
    med = median(nddie, na.rm = TRUE),
    max = max(nddie, na.rm = TRUE),
    min = min(nddie, na.rm = TRUE),
    missval = sum(is.na.data.frame(nddie)),
    samp_size = length((nddie)[!is.na(nddie)])
  ) 
sum_nddie_16up
```


_Summary of abnas memory_
```{r}
abnas_memory = migraine_data %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(abnas_memory, na.rm = TRUE),
    sd = sd(abnas_memory, na.rm = TRUE),
    med = median(abnas_memory, na.rm = TRUE),
    max = max(abnas_memory, na.rm = TRUE),
    min = min(abnas_memory, na.rm = TRUE),
    missval = sum(is.na.data.frame(abnas_memory)),
    samp_size = length((abnas_memory)[!is.na(abnas_memory)])
  )
abnas_memory
```


_Summary of abnas language_
```{r}
abnas_language = migraine_data %>% 
  group_by(., migraine) %>% 
  summarise(
    mean = mean(abnas_language, na.rm = TRUE),
    sd = sd(abnas_memory, na.rm = TRUE),
    med = median(abnas_memory, na.rm = TRUE),
    max = max(abnas_memory, na.rm = TRUE),
    min = min(abnas_memory, na.rm = TRUE),
    missval = sum(is.na.data.frame(abnas_memory)),
    samp_size = length((abnas_memory)[!is.na(abnas_memory)])
  )
abnas_language
``` 

### Historgram 



```{r Histogram of CESD}
hist(subset(migraine_data, migraine == '0')$cesd, xlim = c(0, 50), ylim = c(0, 120), xlab = "", col = "dodgerblue1",  main = "")
par(new = TRUE)
hist(subset(migraine_data, migraine == '1')$cesd, xlim = c(0, 50), ylim = c(0, 120), xlab = "Score", col = "dodgerblue4", main = "Histogram of CESD")
legend("topright", pch = c(15,15), col = c("dodgerblue1", "dodgerblue4"),
       legend = c("No Migraine", "Migraine"))

```




```{r Histogram of NDDIE}
hist(subset(migraine_data, migraine == '0')$nddie, xlim = c(0, 25), ylim = c(0, 100), breaks = 15, xlab = "", col = "goldenrod4",  main = "")
par(new = TRUE)
hist(subset(migraine_data, migraine == '1')$nddie, xlim = c(0, 25), ylim = c(0, 100), breaks = 15, xlab = "Score", col = "goldenrod1", main = "Histogram of NDDIE")
legend("topright", pch = c(15,15), col = c("goldenrod4", "goldenrod1"),
       legend = c("No Migraine", "Migraine"))
```




```{r Histogram of abnas memory}
hist(subset(migraine_data, migraine == '0')$abnas_memory, xlim = c(0, 15), ylim = c(0, 160), breaks = 17, xlab = "", col = "aquamarine4",  main = "")
par(new = TRUE)
hist(subset(migraine_data, migraine == '1')$abnas_memory, xlim = c(0, 15), ylim = c(0, 160), breaks = 17, xlab = "Score", col = "aquamarine1", main = "Histogram of abnas memory")
legend("topright", pch = c(15,15), col = c("aquamarine4", "aquamarine1"),
       legend = c("No Migraine", "Migraine"))
```




```{r Histogram of abnas language}
hist(subset(migraine_data, migraine == '0')$abnas_language, xlim = c(0, 10), ylim = c(0, 160), breaks = 10, xlab = "", col = "darkslategrey",  main = "")
par(new = TRUE)
hist(subset(migraine_data, migraine == '1')$abnas_language, xlim = c(0, 10), ylim = c(0, 160), breaks = 10, xlab = "Score", col = "darkslategray4", main = "Histogram of abnas language")
legend("topright", pch = c(15,15), col = c("darkslategrey", "darkslategray4"),
       legend = c("No Migraine", "Migraine"))
```






